Approximation as Differentiation notes

### 2025-02-24 notes/definitions.tex
Consolidate propositions about CMon-enriched categories and biproducts.

In $\Fam(C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and an indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

We note that if a category $C$ is \emph{$\CMon$-enriched}, we have that:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

\begin{proposition}
Suppose $C$ a $\CMon$-enriched monoidal category.
\begin{itemize}
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}

@@

Any category with biproducts has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A \oplus
B, i_A, i_B)$.

>>>>

In $\Fam(C)$ we then have that:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and an indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with a morphism $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

@@

We note that if a category $C$ is $\CMon$-enriched, then:
\begin{enumerate}
\item Every hom-object $\Hom{C}{A}{B}$ is a commutative monoid of morphisms; we write $\zero_{A,B}$ (zero
morphism) for the unit, and $+_{A,B}$ (addition of morphisms) for the binary operation.
\item Composition is \emph{biadditive}, i.e.~given by a family of morphisms $\Hom{C}{B}{C} \tensor
\Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$ that preserve the additive structure in $\Hom{C}{B}{C}$ and
$\Hom{C}{A}{B}$ separately:

@@

@@

\begin{proposition}
\item
\begin{itemize}
\item If $C$ has biproducts then it has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A
\oplus B, i_A, i_B)$.
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}
